\bf\mftitle

### 2011-03-02 doc/jInfer/paper/paper.tex
Project Web: removing empty.html_. Documentation: fixing title in "paper".
minor

\def\mftitle{jInfer XML schema inference framework}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\section*{Introduction}
Although many algorithms (\cite{ahonen, Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964, 1802522, vyhnanovska})

@@

>>>>

\def\mftitle{jInfer XML Schema Inference Framework}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\section*{Introduction}
Although many algorithms (\cite{ahonen, Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964, 1802522, vyhnanovska}) 
% TODO name all papers
try to solve problem of infering schema for existing set of XML documents, have you ever tried to sovle the problem in practice?

When the problem arises, one wants to find solution as quickly as possible, without need to investigate many scientific papers.
We focus on this group of potential users - programmers, system administrators, xml coders, xml maintaners in private and scientific sector.

Framework is designed extensible and is implemented as a set of plug-ins for NetBeans platform.
This brings second group of users (although much smaller in counts) of framework - scientific developers willing to experiment with their new algorithms may easily gain benefits of user interface provided, thus speeding up their development, easing them comparison with other algorithms already developed for framework.

But it is not all about user interface.
We bring in XML/XSD/DTD import/export modules ready to use.
We implement sample infering algorithm (see \cite{ahonen}).
We provide visualization tools to visualize input XML documents as a set of grammar rules, and tools to visualize non-deterministic finite automatons used in many of infering algorithms.
Thus extending existing NFA base algorithm with user interaction is made simple for scientific developers.

@@

\section*{Short architecture overview}

\section*{More work/Open issues}

\section*{Conclusion?}
